---
title: "R Notebook"
output: html_notebook
---

Minature performes dimensionality reduction on a low-resolution representation of a highly multiplexed imaging dataset in order to provide a thumbnail that represents the spatial heterogenity in the dataset.

Points are coloured by translating their position in 3D low dimension space to a LAB colour. As this is broadly perceptually uniform, similar colours will be closely localised in low-dimension space and therefore have a more similar marker expression signature.

Minature requires: 
- EBImage
- tidyverse
- scales
- dynutils
- colorspace
- uwot

```{r}
test_paths <- list.files(here::here("data"), full.names = TRUE)
```

```{r}

source('~/miniature/R/paint_minaiture.R')

```

```{r}
paint_miniature(test_paths[1], "~/miniature/outputs/test2.png", remove_bg = FALSE)
```

```{r}
tibble(input = test_paths) %>%
  mutate(
    outputs = basename(input) %>% paste0("~/miniature/outputs/",.) %>% str_remove(".ome.tif*") %>% paste0(.,"-miniature.png"),
    painting = map2(input, outputs, paint_miniature)
  ) 
```

```{r}
tibble(input = test_paths) %>%
  mutate(
    outputs = basename(input) %>% paste0("~/miniature/outputs/",.) %>% str_remove(".ome.tif*") %>% paste0(.,"-miniature.png"),
    images = map(outputs, readImage)
  ) %>%
  pull(images) %>%
  map(display, method = "raster") 
```

Current limitation is that the image has to be loaded into memory