---
title: "R Notebook"
output: html_notebook
---

Minature performes dimensionality reduction on a low-resolution representation of a highly multiplexed imaging dataset in order to provide a thumbnail that represents the spatial heterogenity in the dataset.

Points are coloured by translating their position in 3D low dimension space to a LAB colour. As this is broadly perceptually uniform, similar colours will be closely localised in low-dimension space and therefore have a more similar marker expression signature.

Minature requires: 

```{r}



library(EBImage)
library(tidyverse)
library(scales)
library(dynutils)
library(colorspace)
library(uwot)

```

```{r}
test_paths <- list.files(here::here("data"), full.names = TRUE)
```

```{r}

source('~/miniature/R/paint_minaiture.R')

```

Default settings output to a tempfile, the path of which is returned

The default image size has the longest dimension set at 400 px - a comprimise for speed and quality.

Future versions should look to pull a set level of the image pyramid
Note that exact colours and embedding may vary with runs as `fast_sgd` has been set to `TRUE` in `uwot::umap` which accelerates embedding at the cost of exact reproducibility.

```{r}

example_miniature <- paint_miniature(
  input = test_paths[2],
  output = tempfile(fileext = ".png"),
  output_max_dim = 400,
  remove_bg = TRUE,
  return_objects = FALSE
)


example_miniature %>% readImage() %>% display(method = "raster")
```

Mapping accros several examples with default settings

```{r}
tibble(input = test_paths) %>%
  mutate(
    outputs = basename(input) %>% paste0("~/miniature/outputs/",.) %>% str_remove(".ome.tif*") %>% paste0(.,"-miniature.png"),
    painting = map2(input, outputs, paint_miniature)
  ) 
```

Displaying these examples
```{r}
tibble(input = test_paths) %>%
  mutate(
    outputs = basename(input) %>% paste0("~/miniature/outputs/",.) %>% str_remove(".ome.tif*") %>% paste0(.,"-miniature.png"),
    images = map(outputs, readImage)
  ) %>%
  pull(images) %>%
  map(display, method = "raster") 
```



## Getting low dimensional embedding for further plotting

Setting `return_objects == TRUE` returns the processed data to enable further visualisation of the low dimension space
```{r}
miniature_objects <- paint_miniature(
  test_paths[2], 
  return_objects = TRUE, 
  output_max_dim = 300
  )
```
Plot the image and embedding in low-dimension space (3D embedding, Dim1 and Dim2 shown)

```{r}

grid <- miniature_objects$small_image$small_image %>% normalize(ft = c(-0.1,5)) %>%
  display(all = TRUE, method = "raster", nx = 3)

```

```{r}

patchwork::wrap_plots(
miniature_objects$plot$plot,

miniature_objects$plot$umap_colours %>%
  ggplot(aes(V1,V2,colour = LabHexUMAP)) +
  geom_point(shape = ".") +
  coord_equal() +
  scale_colour_identity() +
  theme_classic()

)


```

## Background removal

By default `paint_miniature` attempts background removal using Otsu's threshold on the log scaled channel sum image
This can be acccessed through the small_image slot

```{r}

miniature_objects$small_image$otsu_image %>% display(method = "raster")

```

Background subtraction can be turned off by setting `remove_bg` as FALSE

```{r}
bg_retained <- paint_miniature(
  test_paths[2], 
  remove_bg = FALSE,
  output_max_dim = 300
  ) %>%
  readImage() %>%
  display(method = "raster")
```

